---
title: "HW1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HW1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # I asked chat how to do this because initially my knitted graph
  # is very small and is squeezed to left
  fig.width = 7,
  fig.height = 5
)
```

```{r setup}
source("https://raw.githubusercontent.com/linnykos/561_s2025_public/main/HW1_files/generate_data.R")
```

## Q0

### 0A

Gaia Xu, she/her pronouns 

### 0B

I have read and understood the entire syllabus

### 0C

I've taken many stats courses using R as a UW undergraduation stats student

### 0D

I am really interested in making my own packages and upload it online, so anything will be helpful!

## Q2

### 2A

the input is a integer representing the amount of observations generated, so how long the generated vector is. The output is a vector of numbers that follows distribution of one of a N(10,1), Gamma(2,2), or Chisq(3) distribution.

### 2B

```{r}
set.seed(1)
t <- 10000
nlist <- c(1,2,3,5,10,100)
par(mfrow = c(2, 3))
for (j in 1:6){
  datalist <- rep(NA, t)
  for (i in 1:t){
    n <- nlist[j]
    datalist[i] <- mean(generate_data(n))
  }
  hist(datalist, main=paste0("Sample size: ", n), xlab = "Value")
}
```

### 2C

The plot shows that no matter what the distribution of data is, even if the data does not actually follow one distribution, as sample size increase, in the long run, the mean of the data will converge to a normal distribution.

## Q3

### 3A

```{r}
df <- read.csv("https://raw.githubusercontent.com/linnykos/561_s2025_public/main/HW1_files/sea-ad.csv")
```

The head() shows the first 6 rows of the data. summary() summarize each columns. If the column is numeric, then if provides some property of the numeric data, like mean and median and quantiles. If the column is character, then just show it is character.

### 3B

```{r}
dim(df)
class(df)
```

The dimentionality if 84, 7, and the class is data.frame.

### 3C

```{r}
df$Age.at.Death <- ifelse(df$Age.at.Death == "90+", 90, df$Age.at.Death)
df$Age.at.Death <- as.numeric(df$Age.at.Death)
hist(df$Age.at.Death, main = "Histogram of doner age", xlab = "Doner age")
```

### 3D

```{r}
df$Sex <- as.numeric(df$Sex == "Female")
df$APOE4.Status <- as.numeric(df$APOE4.Status == "Y")
df$Cognitive.Status <- as.numeric(df$Cognitive.Status == "Dementia")
df$Braak <- as.numeric(as.factor(df$Braak))
```

### 3E

```{r}
summary(df)
```

### 3F

```{r}
my.table.braak <- table(df$Braak, df$Cognitive.Status)
colnames(my.table.braak) <- c("no dementia", "dementia")
my.table.braak
```

### 3G

```{r}
score.quantile <- quantile(df$Last.CASI.Score, na.rm = TRUE)
df$Score.Quantile <- cut(df$Last.CASI.Score, score.quantile)
my.table.score <- table(df$Score.Quantile, df$Cognitive.Status)
colnames(my.table.score) <- c("no dementia", "dementia")
my.table.score
```





