---
title: "Clique Analysis Vignette"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Clique Analysis Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## This vignette demonstrates how to:

> Generate a graph with a random partial clique

> Compute the maximal partial clique

> Run a small simulation study to compare methods

> All examples use functions defined in this package.

## load the package

```{r}
library(UWBiost561)
```


## Generate a partial clique

Use generate_partial_clique to generate a graph with 10 nodes, edge prob 0.5, weight threshold 0.95

```{r}
set.seed(10)
g <- generate_partial_clique(n = 10, clique_fraction = 0.5, clique_edge_density = 0.95)
print(g)
```

## Compute a maximal partial clique

Following code runs the 11th implementation on the generated adj matrix and find the partical clique

```{r}
result <- compute_maximal_partial_clique_master(adj_mat = g$adj_mat, alpha = 0.9, number=11,time_limit = 10)
print(result)
```

## Simulation study

```{r}
set.seed(10)
sim_result <- run_simulation(trials=2, clique_edge_density_vec = c(0.95, 0.9), alpha = 0.95, time_limit = 30, imp_numbers = 1:3)
print(sim_result$`clique_edge_density:0.3`$`Trial:1`$Method_1)
```
